\chapter*{Abstract}
Conformal blocks are building blocks of correlation functions in conformal field theories. They neatly encode the universal information dictated by conformal symmetry and separate it from the dynamical information which depends on the particular theory. Conformal blocks merit an in-depth study as is evidenced by their extensive applications in the study of bulk locality in the AdS/CFT correspondence and the recent Conformal Bootstrap program. The vacuum Virasoro blocks in the semi-classical (large central charge) limit is known to compute the leading order contribution to the R\'{e}nyi entropy. Moreover, the semi-classical Virasoro blocks along with conformal bootstrap feature in a proof of the cluster decomposition principle for AdS$_3$/CFT$_2$. 


Conformal field theory and its necessary ingredients are briefly reviewed. 3D gravity including its Chern-Simons formulation are briefly introduced. Conformal blocks from the exchange of a spinless operator are evaluated by holographic computations of geodesic Witten diagrams for AdS$_{n+1}$/CFT$_n$. The results are verified against the Casimir operator method of Dolan and Osborn. The procedure is extended to exchange of a spinning operator. Virasoro blocks in various semi-classical limits are discussed and connection is made with the Chern-Simons formulation of 3D gravity. Expressions for perturbative scalar (corresponding to exchange of spinless operator) Virasoro blocks are calculated in the global and heavy-light limit using the holographic approach. The results are extended to Virasoro blocks for the exchange spinning operators, and the results are verified using the monodromy method.


The Virasoro blocks thus obtained are used to calculate the two interval R\'{e}nyi entropy. A brief introduction is presented to the Conformal Bootstrap, followed by explicit derivation of the Cluster Decomposition principle for AdS$_3$/CFT$_2$.




\iffalse
The focus in the first part is on providing the relevent background. Starting with an introduction to the necessary ingredients from conformal field theory, including Zomolodchokov's recursion relations. Mellin representations of conformal correlation functions and Witten diagrams are discussed. Virasoro blocks are discussed in the different semi-classical limits. Perturbative Virasoro blocks corresponding to the exchange of a spin-less operator are computed in the heavy-light and global limits. The results are extended to Virasoro blocks arising from the exchange of an operator carrying spin. The calculations are done using AdS$_3$/CFT$_2$ holographic computations. For the heavy-light limit, the idea is calculating geodesic Witten diagrams for the light operators interacting in a background created by letting the heavy operators backreact. The geometry thus obtained can be either a BTZ black hole or a conical defect in AdS$_3$.

Lastly, applications to calculating two interval R\'{e}nyi entropy are discussed. Also, using the Conformal Bootstrap to constrain operator dimensions in CFTs is briefly introduced.
\fi